---
title: "Comparing spectral skies"
author: "Priji Balakrishnan"
date: "3/12/2020"
output: github_document
---

We load the following libraries for our analysis.

```{r message=FALSE}
library(tidyverse)
library(lubridate)
library(here)
```

```{r include=FALSE}
knitr::opts_chunk$set(dpi=300)

newtheme <- theme_grey() +
  theme(axis.line.x = element_line(size=0.8, colour = "black"),
        axis.line.y = element_line(size=0.8, colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        # panel.border = element_rect(linetype = "solid", fill = NA, size = 1),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 10, face = "bold"),
        text = element_text(size=10),
        legend.position = "bottom",
        legend.title =element_blank(),
        axis.title=element_text(size=10),
        axis.text.x=element_text(colour="black", size = 9),
        axis.text.y=element_text(colour="black", size = 9))
theme_set(newtheme)
```

We load the data.

```{r}
singapore_skies <- readRDS(here::here("resources/processed_data/singapore.rds"))
berlin_skies <- readRDS(here::here("resources/processed_data/berlin.rds"))

spectral_skies <- singapore_skies %>%
  bind_rows(berlin_skies) %>%
  arrange(loc, hour(datetime), SkyType, wv) %>%
  mutate(measurement = as_factor(str_c(loc, as.character(datetime), SkyType, sep="-")))
```

All experiments:

```{r}
levels(spectral_skies$measurement)
```


The following notebook expects data according to the following schema:

- `wv`
- `spd`
- `SkyType`
- `CCT`
- `loc`
- `datetime`: date format

## Comparison between different Singapore morning skies

We subset the data to get measurements in Singapore during the morning.

```{r}
singapore_morning <- spectral_skies %>%
  filter(loc == "SIN", hour(datetime) <= 11)
```

```{r}
singapore_morning %>%
  ggplot() +
  geom_line(aes(x = wv, y = spd, group = measurement, color = measurement))
```

## Comparison between Singapore and Berlin

```{r}
mornings <- spectral_skies %>%
  filter(SkyType == "CS" | str_starts(SkyType, "MS"), hour(datetime) >= 7, hour(datetime) <= 10,
         loc == "BER" | (loc == "SIN" & month(datetime) == 2))
```

```{r}
mornings <- spectral_skies %>%
  filter(hour(datetime) >= 7, hour(datetime) <= 10,
         loc == "BER" | (loc == "SIN" & month(datetime) == 2))
```

```{r}
mornings %>%
  ggplot() +
  geom_line(aes(x = wv, y = spd, group = measurement, color = measurement))
```

```{r}
mornings %>%
  filter(wv == 560) %>%
  select(wv, measurement, spd) %>%
  inner_join(mornings, by = c("measurement")) %>%
  mutate(normalised_spd = spd.y / spd.x) %>%
  select(-wv.x, -spd.x, wv = wv.y, spd = spd.y) %>%
  ggplot() +
  geom_line(aes(x = wv, y = normalised_spd, group = measurement, color = measurement)) +
  geom_vline(xintercept = 725, linetype = 3, size = 0.2)+
  annotate(geom = "text", x = 725, y = 1.2, label = "Water vapour  725nm", 
           color = "black", angle = 90, size = 2.7, hjust = 1, vjust = -0.4)
```

