---
title: "Processing Berlin data"
author: "Priji Balakrishnan"
date: "3/12/2020"
output: github_document
---



Load libraries

```{r message=FALSE}
library(tidyverse)
library(lubridate)
library(here)
```

```{r include=FALSE}
knitr::opts_chunk$set(dpi=300)

newtheme <- theme_grey() +
  theme(axis.line.x = element_line(size=0.8, colour = "black"),
        axis.line.y = element_line(size=0.8, colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        # panel.border = element_rect(linetype = "solid", fill = NA, size = 1),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 10, face = "bold"),
        text = element_text(size=10),
        legend.position = "bottom",
        legend.title =element_blank(),
        axis.title=element_text(size=10),
        axis.text.x=element_text(colour="black", size = 9),
        axis.text.y=element_text(colour="black", size = 9))
theme_set(newtheme)
```

### Load data

```{r message=FALSE}
a <- read_csv(here::here("resources/berlin/25feb19-0907-CS-5826K.csv")) %>%
  mutate(loc = "BER",
         datetime = ymd_hms("2019-02-25 09:07:00"),
         SkyType = "CS",
         CCT = 5826)
b <- read_csv(here::here("resources/berlin/25feb19-1200-CS-5607K.csv")) %>%
  mutate(loc = "BER",
         datetime = ymd_hms("2019-02-25 12:00:00"),
         SkyType = "CS",
         CCT = 5607)
c <- read_csv(here::here("resources/berlin/25feb19-1500-CS-5753K.csv")) %>%
  mutate(loc = "BER",
         datetime = ymd_hms("2019-02-25 15:00:00"),
         SkyType = "CS",
         CCT = 5753)

berlin_skies <- a %>%
  bind_rows(b) %>%
  bind_rows(c)
```

Save the data as an RDS object.

```{r}
saveRDS(berlin_skies, here::here("resources/processed_data/berlin.rds"))
```

### Explore data

```{r}
berlin_skies %>% glimpse()
```

Description of the variables:

- **wv**: Wavelength in nm (nanometers)
- **spd**: Spectral irradiance measured in W/m<sup>2</sup>/nm
- **loc**: Location code for Berlin
- **datetime**: Date and time of measurement taken in YY-MM-DD HH:MM:SS
- **SkyType**: Sky condition code--Clear Sky (CS)
- **CCT**: Colour temperature of the measured sky in Kelvin (K)

The measurements were taken at three different times of the day--morning (9am), noon (12pm), and evening (3pm).

```{r}
berlin_skies %>% 
  select(datetime) %>%
  distinct()
```

```{r}
berlin_skies %>%
  mutate(datetime = as.character(datetime)) %>%
  ggplot() +
  geom_line(aes(x = wv, y = spd, group = datetime, colour = datetime)) +
  scale_color_brewer(palette = "Dark2") +
  xlab("Wavelength (nm)") +
  ylab("Spectral irradiance (W/m2/nm)")
```

